16th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
Updated the link for cloud & parallel track info
remove draft
Fix title

\usepackage{draftwatermark}
%\usepackage{showframe}   % debug

@@

\title{15th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2021): Rules and Procedures}

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2021/news/2021-02-05-parallel-and-cloud-tracks}.

>>>>

%\usepackage{draftwatermark}
%\usepackage{showframe}   % debug

@@

\title{16th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2021): Rules and Procedures}

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.
